---
title: "STA6990: Week 1"
author: "Your Name Here"
execute:
  echo: true
  warning: false
  message: false
format: 
  html:
    embed-resources: true
editor: source
---

<!-- This is a HTML comment. It will not appear in the rendered file. -->

```{r example}
# this is a R comment. it will show in the rendered file when the chunk is set to display
# for this file, we have the default chunk option set to display (controlled by the `echo` option in the yaml)

# this differently colored section is called a code chunk
# we can add code chunks using the green button with a C on it in the toolbar
# we can also add code chunks using a keyboard shortcut.

# at the beginning of the chunk, we told the file that it needs to use R to analyze what is here
# we also gave the chunk a name; you can see the chunks and their names at the bottom of this panel
```

```{r no_show}
#| echo: false # this is a chunk option
# by setting echo to false, we are telling Quarto to suppress this code chunk in the output
```

```{r setup}
library(tidyverse)
# if the above line throws an error, remove the # from the next line and run it
# install.packages("tidyverse")
# once library(tidyverse) works, delete the commented section here
# leaving certain commands in a .qmd file will keep it from rendering properly
# view(dataframe) is another one that will prevent rendering
```

**1. What is your name? Change the font color to be your favorite color. Note: this is asking for you to write HTML code. It is *not* R code.**

***Dr. Seals***

1.  First question

2.  Second question

-   Bullet 1

-   Bullet 2

| Col1   | Col2     | Col3     |
|--------|----------|----------|
| Cell 1 | Cell 2   | Cell 3   |
|        | Cell 2.1 |          |
|        |          | Cell 3.2 |

<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-0pky{border-color:inherit;text-align:left;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-0pky">whee</th>
    <th class="tg-0pky"></th>
    <th class="tg-0pky"></th>
    <th class="tg-0pky"></th>
    <th class="tg-0pky"></th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-0pky"></td>
    <td class="tg-0pky">test</td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
  </tr>
  <tr>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
  </tr>
  <tr>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
  </tr>
</tbody>
</table>


<style type="text/css">
.tg  {border-collapse:collapse;border-spacing:0;}
.tg td{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  overflow:hidden;padding:10px 5px;word-break:normal;}
.tg th{border-color:black;border-style:solid;border-width:1px;font-family:Arial, sans-serif;font-size:14px;
  font-weight:normal;overflow:hidden;padding:10px 5px;word-break:normal;}
.tg .tg-0pky{border-color:inherit;text-align:left;vertical-align:top}
</style>
<table class="tg">
<thead>
  <tr>
    <th class="tg-0pky" colspan="2">whee</th>
    <th class="tg-0pky"></th>
    <th class="tg-0pky"></th>
    <th class="tg-0pky"></th>
  </tr>
</thead>
<tbody>
  <tr>
    <td class="tg-0pky"></td>
    <td class="tg-0pky">test</td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
  </tr>
  <tr>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
  </tr>
  <tr>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
    <td class="tg-0pky"></td>
  </tr>
</tbody>
</table>

$$
\begin{tabular}{|ll|l|l|l|}
\hline
\multicolumn{2}{|l|}{whee}    &  &  &  \\ \hline
\multicolumn{1}{|l|}{} & test &  &  &  \\ \hline
\multicolumn{1}{|l|}{} &      &  &  &  \\ \hline
\multicolumn{1}{|l|}{} &      &  &  &  \\ \hline
\end{tabular}
$$

**2. Is there a nickname you go by that you would like to go by in the classroom? Change the font to be Italicized.**

Dr. Seals

**3. What are your career goals after you are finished with the program? Change the font to be underlined.**

When I was in your shoes (finishing a master's degree here at UWF), I knew I wanted to teach at the university level... so going after a PhD was my next step. I was fortunate to be able to choose between programs in mathematics, statistics, and biostatistics.

**4. What questions do you have about this course? Write them using an enumerated list.**

Insert your answers here :)

a.  Test
b.  Test 2
c.  Test 3

**5. What is the keyboard shortcut to render this file?**

Insert your answer here :)

**6. Render this file using the keyboard shortcut and tell me where the resulting .html file saved to.**

Insert your answer here :)

**7. What is the keyboard shortcut to add a code chunk?**

Insert your answer here :)

Insert code chunk here. Add your favorite animal as a comment inside of the chunk.

**8. What is the keyboard shortcut to run a single line within a code chunk?**

Insert your answer here :)

**9. Import the dataset located on Canvas.**

Insert your answer here :)

**10. Find an interesting (to you!) dataset from [Tidy Tuesday](https://github.com/rfordatascience/tidytuesday) and import it here.**

Insert your answer here :)

**11. Use functions within `tidyverse` to find an appropriate summary statistic for one variable in the dataset. Hint: Dr. Google is your friend! Try searching "summary statistic tidyverse".**

Insert your answer here :)

**12. Bonus! Use `ggplot()` to construct a visualization relevant to the dataset.**

Insert your answer here :)
